---
title: "A04_G40116958.rmd"
author: "minxuan"
date: "September 28, 2017"
output: html_document
---

```{r}
library(dplyr)
library(tibble)
library(xtable)
library(ggplot2)
```

## Part A

# Read the data
# You download this file from https://www.kaggle.com/ludobenistant/hr-analytics
# and use your own path 

```{r}
mydf <- read.csv("~/HR_comma_sep.csv")
```

# get rows and columns

```{r}
dim.data.frame(mydf)
```

# explore the data structure

```{r}
str(mydf)
```

# Correlate all the numeric fields

```{r}
xtable(cor(subset(mydf, select = -c(sales, salary))))
```

# Create a correlation heat map

```{r}
library(reshape2)
melted_cormat <- melt(cor(subset(mydf, select = -c(sales, salary))))
head(melted_cormat)

g <- ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_raster()
g <- g + theme(axis.text.x = element_text(angle = 90, hjust = 1))
g
```

# Develop a 3-way table

```{r}
mydf$status <- ifelse(mydf$left == 1, "Left", "Stay")
table(mydf$status,  mydf$salary, mydf$sales)
```

# Employees who leave by department

```{r}
ggplot(mydf[ which(mydf$status=='Left'),], 
       aes(x = sales, fill = status)) + geom_bar() + guides(fill=FALSE) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```

# Complete this for employees who stay in the company by department

```{r}
ggplot(mydf[ which(mydf$status=='Stay'),], 
       aes(x = sales, fill = status)) + geom_bar() + guides(fill=FALSE) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```


## Part B

# Complete this for employees who leave the company by salary level 

```{r}
ggplot(mydf[ which(mydf$status=='Left'),], 
       aes(x = salary, fill = status)) + geom_bar() + guides(fill=FALSE) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```

# Complete this for employees who stay in the company by salary level 

```{r}
ggplot(mydf[ which(mydf$status=='Stay'),], 
       aes(x = salary, fill = status)) + geom_bar() + guides(fill=FALSE) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```

# Make a chart for number of employees who leave the company by time spent in the company
# faceted by salary level AND department

```{r}
ggplot(mydf[ which(mydf$status=='Left'),], 
       aes(x = time_spend_company, fill = status)) + geom_bar() + guides(fill=FALSE) +
  facet_grid(salary~sales)
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```

# Make a chart for number of employees who who stay in the company by time spent in the company 
# faceted by salary level AND department

```{r}
ggplot(mydf[ which(mydf$status=='Stay'),], 
       aes(x = time_spend_company, fill = status)) + geom_bar() + guides(fill=FALSE) +
  facet_grid(salary~sales)
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```


## Part C
# Draw a bar plot of how many years did employees stay in the company before leaving
# Year stayed in the company is the x axis

```{r}
ggplot(mydf[ which(mydf$status=='Left'),], 
       aes(x = time_spend_company, fill = time_spend_company)) + geom_bar() + guides(fill=FALSE) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# Draw a bar plot of how many years did employees stay in the company before leaving
# by department
# Year stayed in the company is the x axis

```{r}
ggplot(mydf[ which(mydf$status=='Left'),], 
       aes(x = time_spend_company, fill = time_spend_company)) + geom_bar() + guides(fill=FALSE) + facet_grid(.~sales)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# Draw a bar plot of how many years did employees stay in the company before leaving
# by salary level
# Year stayed in the company is the x axis

```{r}
ggplot(mydf[ which(mydf$status=='Left'),], 
       aes(x = time_spend_company, fill = time_spend_company)) + geom_bar() + guides(fill=FALSE) + facet_grid(.~salary)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
